\section{Experience}

\vspace{1mm}
\subsection{\textbf{Accademic Work Projects}}

\cventry{09/2022 - 12/2022}
    {Control System Engineer \& Computer Vision Specialist - Student}
    {Laboratory of Robotics Moscow Polytechnic University}
    {
    \newline
    Autonomous Transport Systems Project
    \href{https://disk.yandex.ru/d/LFgKC8DGddJJog}{\textcolor{blue}{Ressources}} With \href{https://vk.com/id194268921}{\textcolor{blue}{Maxim Arkhipov}} and \href{https://vk.com/id104681675}{\textcolor{blue}{Lada Matrosova}}}
    {Moscow, Russia}
    {
    In this project, I worked as part of a team to continu the development of the autonomous transport system capable of transferring cubic objects from the ground to a designated location where they would be picked up by a drone.        
    As part of an university project, I was assigned to these following responsibilities:
    \begin{itemize}
        \item Code the control logic to maneuver a robotic crane (x, y, z axes movements) with an electromagnet actuator to pick up objects
        \item Program the activation and deactivation of the electromagnet to grip and release objects
        \item Code the object conveyor belt, escalator, and launching mechanisms using Raspberry Pi GPIO
        \item Rewrite functions to optimize crane and transport component movements
        \item Create a continuous loop system to pick up objects, transport them through various stages, and deliver them to the drone pad
        \item Implemented OpenCV algorithms for real-time object detection and center point identification through a camera feed
    \end{itemize}
    \vspace{2mm}
    Skills Used:
    \begin{itemize}
        \item Troubleshooting - diagnosed and repaired various sensors and mechanisms
        \item Python - for overall system programming and RPi GPIO control
        \item OpenCV - for computer vision and object detection
        \item RPi GPIO - for interfacing with and controlling sensors and hardware
        \item System optimization - rewrote functions for smoother component movements
        \item Collaborative problem-solving and teamwork
    \end{itemize}
    \vspace{1mm}
    Outcomes:
    \begin{itemize}
        \item Gained valuable experience in robotic manipulations, object transport mechanisms, computer vision, and Python/RPi programming
        \item The system can successfully identify, pick up, and transport a variety of objects to the drone pad autonomously
    \end{itemize}
    }

\vspace{2mm}

\cventry{03/2022 - 06/2022}
    {Software and Control System Engineer - Student}
    {\href{https://mospolytech.ru/dovuzovskoe-obrazovanie/laboratoriya-letayushchej-robototekhniki/}{\textcolor{blue}{Laboratory of Flying Robotics COEX (COPTER EXPRESS)}} - Moscow Polytechnic University}
    {
    \newline
    ROVER Project
    \href{https://disk.yandex.ru/d/_G7udE6qSE2OYg}{\textcolor{blue}{Ressources}} With \href{https://t.me/PavelShi}{\textcolor{blue}{Pavel Shishkin}}
    }    
    {Moscow, Russia}
    {
    As part of an university project, I was assigned to these following responsibilities:
    \begin{itemize}
        \item Repairing and replacing damaged or malfunctioning components in the ROVER's internal circuitry, including drivers, matrices, batteries, transmitters, receivers, and other essential parts.
        \item Developing and implementing a code to control the movement of six wheels using a RC controller \href{https://clover.coex.tech/en/radio.html}{\textcolor{blue}{FLYSKY RC}}
        \item Connecting \href{https://learn.adafruit.com/32x16-32x32-rgb-led-matrix/how-the-matrix-works}{\textcolor{blue}{matrix}} LEDs to display predefined images.
        \item Installing and configuring ROS on a Raspberry Pi to enable real-time data transfer over the internet.
        \item Integrating the ROS system with an Arduino board to allow for seamless communication between the two devices.
    \end{itemize}
    \vspace{2mm}
    Skills Used:
    \begin{itemize}
        \item Troubleshooting and repair of electronic circuits
        \item Programming and coding (RC controller, Arduino, ROS)
        \item Sensor and actuator integration and control (BeeRotor, IBT\_2)
        \item Real-time operating systems and data transmission
        \item Collaborative problem-solving and teamwork
    \end{itemize}
    }        


\vspace{2mm}

\cventry{03/2021 - 06/2021}
    {Computer-Aided Design Engineer - Student}
    {Moscow Polytechnic University}
    {
    \newline
    Development of an Aeroponic Tower System
    \href{https://drive.google.com/drive/folders/1GYReOb4vYT3_jlym9ULB7Yud_lAxtPxk}{\textcolor{blue}{Ressources}}, with Pavel Strokov.
    }
    {Moscow, Russia}
    {
    As part of a university project, I participated in the design and development of an aeroponic tower system. And I was assigned to these following responsibilities:
    \begin{itemize}
        \item Develop the Aeroponic Support 3D model.
        \item Define Materials Required for the aeroponic's construction.
        \item Evaluate the overall weight of the structure.
    \end{itemize}
    }

\vspace{1mm}

\cventry{09/2020 - 12/2020}
    {Electronic and Control System Technician - Student Lead}
    {Moscow Polytechnic University}
    {
    \newline Development of an Water Cleaner Boat}
    {
    \href{https://github.com/DanGlChris/Water-cleaning-boat}{\textcolor{blue}{Ressources}}Moscow, Russia}
    {
    As part of an university project, I lead this project and I was assigned to these following responsibilities:
    \vspace{1mm}
    \begin{itemize}
        \item Create a 3D model of a water cleaning boat using Blender.
        \item Develop a circuit schematic and programmed an Arduino board to control DC motors and other actuators for the boat.
        \item Successfully implement the boat's navigation system, including sensors and control algorithms.
        \item Collaborate with the team to design and test the boat's hardware and software components.
    \end{itemize}
    \vspace{1mm}
    Skills Used:
    \begin{itemize}
        \item 3D modeling and prototyping
        \item Electronics and microcontrollers
        \item Programming languages (Arduino \& C/C++)
        \item Sensor integration and control systems
        \item Leadership, teamwork and collaboration
    \end{itemize}
    }

\vspace{1mm}
\newpage
\subsection{\textbf{Freelance}}

\cventry{2019 - 2022}
    {Graphic Designer}
    {Fiverr \& \href{https://danglchris.netlify.app/}{\textcolor{blue}{DanGlChris}}}
    {Worldwide}
    {
    \newline
    My graphic design services include logo design, branding, flyers and slideshows. I have worked with various clients across different industries, including magazine, food, studio and entertainment. 
    \newline
    I also offer web design services. I have created landing pages, portfolios, and short websites for clients in various fields.
    To view my portfolio, please visit my \href{https://www.behance.net/kankwandadaglox}{\textcolor{blue}{Behance}}, \href{https://dribbble.com/DanGlChris}{\textcolor{blue}{Dribbble}} or 
    \href{https://www.fiverr.com/danglchris/design-in-one-day-a-professional-creative-minimalist-logo-634d?utm_campaign=gigs_show&utm_medium=shared&utm_source=copy_link&utm_term=plvgj8}{\textcolor{blue}{Fiverr}} pages.
    } 
    {\newline
    Notable Achievements:
    \begin{itemize}
        \item Designed logos and brands for several small businesses, creating visually striking and memorable identities.
        \item Created engaging flyers and slideshows for presentations, capturing the essence of my clients' messages and objectives.
        \item Developed professional websites that showcase my clients products or services, leveraging my expertise in web design and user experience.
    \end{itemize}
    \vspace{1mm}
    Skills Applied:
    \begin{itemize}
        \item Logo and brand creation
        \item Flyer and slideshow design
        \item Web design and development (Angular, HTML, SCSS, and JavaScrip - Typescript)
        \item Client communication and collaboration
        \item Photoshop, Illustrator, Figma
    \end{itemize}
    }

\vspace{2mm}

\cventry{08/2023 - 09/2023}
    {Data Analyst \& Graphic Designer}
    {\href{https://www.linkedin.com/posts/daglox-kankwanda-59a617182_package-design-dataset-activity-7105563461622870017-fupP?utm_source=share&utm_medium=member_desktop}{\textcolor{blue}{daglox kankwanda}}}
    {Worldwide}
    {
    \newline
    Projet: Market Trend Analysis and Label Package Design
    \newline
    I Collected data from a digital design market website to identify trends, popular designs, prices, and other key indicators.
    I processed and analyzed data, created visualizations, and drew insights to inform the creation of a label package design.
    Published \href{https://www.kaggle.com/datasets/dagloxkankwanda/package-design-dataset}{\textcolor{blue}{dataset}} and 
    \href{https://www.kaggle.com/code/dagloxkankwanda/packaging-design-analysis}{\textcolor{blue}{the trend analysis notebook}} on Kaggle and 
    \href{https://www.behance.net/gallery/179054409/Label-package-design-templlate?tracking_source=search_projects|Daglox&l=0}{\textcolor{blue}{design}} on Behance
    Attempted to sell the design on various websites (Adobe Stock, Creative Design, Evanto Marketplaces and Other) but faced rejection, so sold the dataset directly on kaggle using Binance.
    } 
    {
    \newline
    Notable Achievements:
    \begin{itemize}
        \item Successfully identified trends and patterns in the digital design market.
        \item Created a visually appealing and informative dataset publication on Kaggle.
        \item Developed a unique label package design template.
        \item Demonstrated perseverance and adaptability in pivoting to sell the dataset after facing rejection
    \end{itemize}
    \vspace{1mm}
    Skills Applied:
    \begin{itemize}
        \item Web Scraping with Selenium.py (Webdriver) and JQuery
        \item Data analysis, processing and visualization
        \item Adobe Illustrator, Kaggle code and Jupyter notebooks
        \item Design thinking, Creative problem-solving, Creativity and Attention to detail.
        \item Entrepreneurial spirit
        \item Understanding for intellectual property and right
    \end{itemize}
    }

\vspace{1mm}
\newpage

\subsection{\textbf{Assistantship}}

\cventry{04/2023 - 09/2023}
    {Senior Python Developer \& Data Scientist Intern}
    {Remote}
    {
    \newline
    Project : Textual Analysis to Machine Learning Model for Predicting Activist Seller Success.
    \href{https://www.linkedin.com/posts/daglox-kankwanda-59a617182_short-activist-predictor-activity-7129183448644083712-BFpY?utm_source=share&utm_medium=member_desktop}{\textcolor{blue}{Ressources}} 
    with \href{https://linkedin.com/in/kiryukhin}{\textcolor{blue}{Oleg Kiriukhin}} \& \href{https://linkedin.com/in/oleg3372}{\textcolor{blue}{Oleg Rogov}}
    }
    {Moscow, Russia}
    {
    As a python developer, assistant researcher and intern data scientist, I worked on a volunteer research project, 
    creating and publishing a machine learning model and Python module for text analysis and prediction. 
    Through this project, I acquired skills in data processing, model implementation, 
    and Python packaging, and developed a deeper understanding of finance and machine learning.
    \newline
    Notable Achievements:
    \begin{itemize}
        \item Collaborated with the research team to create and publish a \href{https://pypi.org/project/short-activist-predictor/}{\textcolor{blue}{Python module}} and machine learning model for text analysis and prediction.
        \item Acquired knowledge in finance (Short Seller Activists) and machine learning to contribute to the project, including data processing, model implementation, and Python packaging.
        \item Utilized cloud-based notebooks, such as Google Colab, to execute experiments and interpret relevant reports.
        \item Developed skills in data processing, model implementation, and Python packaging through hands-on experience and self-study.
        \item Published module on \href{https://github.com/DanGlChris/short_activist_predictor}{\textcolor{blue}{GitHub}} and PyPI, and made the model available on \href{https://huggingface.co/collections/DanGlChris/short-activists-predict-6534a69d1922c31a9b0198f9}{\textcolor{blue}{Hugging Face}}.
    \end{itemize}
    \vspace{1mm}
    Skills Applied:
    \begin{itemize}
        \item Machine learning model development and deployment
        \item Topic modeling with BERTtopic
        \item Financial analysis 
        \item Jupyter notebooks and Cloud-based computing (Google Colab)
        \item Python - PyScaffold, Panda, numpy, plotly, Bertopic, Transformers, Huggingface\_hub, NLTK, Sklearn
        \item Llama integration
        \item Data interpretation, visualization and processing
        \item Team collaboration and communication
    \end{itemize}        
    \vspace{1mm}
    Objective:
    \begin{itemize}
        \item To gain practical experience in machine learning and natural language processing while contributing to a research project focused on predicting activist seller success in the stock market.
    \end{itemize}
    }
    



